2H qSIP Calculations

### 2021-10-18 qSIP_calculations.Rmd
whole-analysis peak table

# focus on not CRC samples
sample_files <- iso_filter_files(sample_files, str_detect(id1, "cri", negate = TRUE))
```

@@

```{r "example_chromatograms", fig.width=8, fig.height=8}
# plot the chromatograms
iso_plot_continuous_flow_data(
  # all sample files
  sample_files,
  # select data and aesthetics
  data = c(2), color = id1, panel = id1,
  # zoom in on time interval
  time_interval = c(750, 4000),
  # peak labels for all peaks > 2V
  peak_bounds = TRUE,
  peak_marker = FALSE,
  peak_label = iso_format(rt),
  #peak_label_size = 3,
  peak_label_filter = analysis == 5685 & amp2 > 1
) + scale_color_npg() + 
  theme_classic() +
  theme(strip.background = element_blank())
```

@@

```{r}
# this information is often maintained in a csv or Excel file instead
# but generated here from scratch for demonstration purposes
peak_map <- 
  readxl::read_excel(file.path("data","IRMS", "peak_map_manual.xlsx"))
peak_map

@@

```{r}
peaks_mapped <- peak_table %>%
  iso_map_peaks(peak_map, map_id = Analysis) %>%
  filter(!is.na(compound))
```

@@

```{r}
# FL = 0.005 # tracer strength = 0.5%
# a = 0.5 # incorporation efficiency of 50%
# FT = 0.02 # resulting isotopic enrichment
# F0 = 0.0124 # beginning isotopic enrichment

@@

@@

@@

peaks_mapped <- peaks_mapped %>%
  group_by(sample_id) %>% 
  mutate(f_start = case_when(
           inc_time_d == 0 ~ at2H,
           inc_time_d != 0 ~ inc_time_zero$at2H
           ),
         terrain = case_when(
           substr(sample_id, 1, 1) == "t" ~ "Tundra",
           substr(sample_id, 1 ,1) == "c" ~ "Alpine Conifer Forest",
           substr(sample_id, 1 ,1) == "m" ~ "Alpine Meadow",
           substr(sample_id, 1 ,1) == "g" ~ "Grassland"))

@@

## Remove standards from gencalcs
```{r}
peaks_mapped_active <- peaks_mapped %>% 
  filter(str_detect(compound, "STD", negate = TRUE))
```

>>>>

# EXCLUDE CRC SAMPLES FROM THIS ANALYSIS
sample_files <- iso_filter_files(sample_files, str_detect(id1, "cri", negate = TRUE))

sample_files <- iso_filter_files(sample_files, str_detect(id1, "cr0", negate = TRUE))

# EXCLUDE C26 ALKANE STANDARD
sample_files <- iso_filter_files(sample_files, str_detect(id1, "C26", negate = TRUE))
```

@@

```{r "example_chromatograms", fig.width=8, fig.height=8}
# plot an example chromatogram

sample_files[10] %>% # choosing arbitrary file to plot
iso_plot_continuous_flow_data(
  # select data and aesthetics
  data = c(2), color = id1, panel = id1,
  # zoom in on time interval
  time_interval = c(750, 4000),
  # peak labels for all peaks > 2V
  peak_bounds = TRUE,
  peak_marker = FALSE,
  peak_label = iso_format(rt),
  #peak_label_size = 3,
  peak_label_filter = analysis == 5685 & amp2 > 1
) + scale_color_npg() + 
  theme_classic() +
  theme(strip.background = element_blank())
```

@@

```{r}
# this information is often maintained in a csv or Excel file
peak_map <- 
  readxl::read_excel(file.path("data","IRMS", "peak_map_manual_general.xlsx"))
peak_map

@@

```{r}
# Generate an isoverse peak map
peaks_mapped <- peak_table %>%
  iso_map_peaks(peak_map, map_id = Analysis) %>%
  filter(!is.na(compound))
```

@@

```{r}
# Define a function to calculate turnover and generation time
# ARGUMENTS:
# FL = 0.005 # tracer strength = 0.5%
# a = 0.5 # incorporation efficiency of 50%
# FT = numeric # resulting isotopic enrichment
# F0 = numeric # beginning isotopic enrichment

@@

```{r}

@@

mtda <- read_csv(file.path("data", "sample_metadata_2021.csv"))
sample_names <- mtda$id1

peaks_mapped <- peaks_mapped %>% 
  filter(sample_id %in% sample_names)

@@

peaks_mapped <- peaks_mapped %>%
  group_by(sample_id) %>%
  mutate(f_start = case_when(
           inc_time_d == 0 ~ at2H,
           inc_time_d != 0 ~ inc_time_zero$at2H
           ),
         terrain = case_when(
           substr(sample_id, 1, 1) == "t" ~ "Niwot Ridge Tundra",
           substr(sample_id, 1 ,1) == "c" ~ "Gordon Gulch Conifer Forest",
           substr(sample_id, 1 ,1) == "m" ~ "Gordon Gulch Meadow",
           substr(sample_id, 1 ,1) == "g" ~ "Marshall Mesa Grassland"))

@@

## Remove standards from gencalcs
```{r}
# Don't want our standard compounds to be used for generation time calculations! x_x
peaks_mapped_active <- peaks_mapped %>% 
  filter(str_detect(compound, "STD", negate = TRUE))
```

Generation time is related to the turnover rate as below:
$$
g = \frac{ln(2)}{\mu}
$$
